Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
fix first sentence in section II

A recent paradigm processes the audio stream in a holistic way over larger time scales, without assuming that a single species is present throughout the recording. Automated systems belonging to this paradigm aim to infer global properties of bioacoustic scenes, including biodiversity indices \cite{Bardeli2010}, migration patterns \cite{Obrist2010}, as well as to detect time regions of particular interest requesting detailed human inspection \cite{rosenstock2002landbird,diefenbach2007incorporating}.

>>>>

A recent paradigm in computational bioacoustics processes the audio stream in a holistic way over larger time scales, without assuming that a single species is present throughout the recording. Automated systems belonging to this paradigm aim to infer global properties of bioacoustic scenes, including biodiversity indices \cite{Bardeli2010}, migration patterns \cite{Obrist2010}, as well as to detect time regions of particular interest requesting detailed human inspection \cite{rosenstock2002landbird,diefenbach2007incorporating}.
